---
title: "Second look at the `rtweet` package"
author: "Patrick Connolly"
date: "`r format(Sys.time(), '%a %d/%m/%Y %H:%M')`"
output: html_document
---
<style type="text/css">
.main-container {
  max-width: 2800px;
  margin-left: auto;
  margin-right: auto;
}
</style>


```{r global_options, echo=FALSE}
knitr::opts_chunk$set(tidy=TRUE,
                      warning=FALSE, 
                      message=FALSE,
                      cache=FALSE,
                      dpi=600)
```
# Scraping tweets from Twitter

Information derived from useR2019_tutorial which has been copied shamelessly

## Packages to install

Install packages `httr`, `jsonlite` if not already installed by uncommenting lines from the following code

### working with APIs

```{r echo = TRUE}
## install.packages("httr")

## install.packages("httpuv") # not sure if this one is needed yet
## install.packages("jsonlite")
```
Likewise with 

### Twitter
```{r}
## install.packages("rtweet")
```

Could be doing media other than twitter, but not yet.

### text analytics
``` {r} 
## install.packages("tidyverse")

## install.packages("tidytext")
## install.packages("devtools")
## devtools::install_github("flovv/RoogleVision")

 ## install.packages("wordcloud2")
 ## install.packages("WriteXLS")
require(httpuv)
require(dplyr)

```
### image analytics
``` {r}
## install.packages("RoogleVision")

```                

(will likely require other dependencies)

### sundry additional packages
```{r}
## install.packages("knitr")

## install.packages("plotly")

## bringLibrary("3.5.0", "3.6.3", "~/local")
## update.packages(ask = FALSE, checkBuilt = TRUE)
```

### Load packages
```{r, cache = TRUE}
library(rtweet)
library(instaR)
library(tidyverse)
library(tidytext)
 library(wordcloud2)
library(RoogleVision)
library(ggplot2)
library(jsonlite)
require(knitr)
require(kableExtra)
require(devtools)

devtools::install_github("flovv/RoogleVision")
```

## Twitter user names that somehow relate to Zespri

 can be found as so:


```{r, cache = TRUE}
Zusrs <- search_users("#zespri", n = 1000)
dim(Zusrs)
colnames(Zusrs)


```
which seem to be the same names of lots of other data frames returned from searches.

library(PFRTextMiner)

require(purrr)
require(tidytext)


## GE insights

```{r new search,  cache = TRUE}
genz <- rtweet::search_tweets(q = "GE new zealand", n = 2500, lang="en")
```

```{r gework, cache= TRUE}
retweet.cols <- c("screen_name", "created_at", "text",  "retweet_text",   
"retweet_created_at",   "is_retweet",  "retweet_screen_name", 
"retweet_name",  "retweet_location",  "retweet_description", "name")
genz.retweet1 <- genz[1:15, retweet.cols[c(1, 5, 2, 7, 8, 11)]]
genz.retweet2 <- genz[1:15, retweet.cols[c(2, 6, 5, 1)]]
genz.retweet3 <- genz[1:15, retweet.cols[c(3, 6, 10,11)]]
 genz.retweet <- genz[, retweet.cols]
knitr::kable(genz.retweet3, format = "html", row.names = TRUE) %>% 
   kableExtra::kable_styling(full_width = FALSE, position = "left")
knitr::kable(genz.retweet2, format = "html", row.names = TRUE) %>% 
   kableExtra::kable_styling(full_width = FALSE, position = "left")
knitr::kable(genz.retweet1, format = "html", row.names = TRUE) %>% 
   kableExtra::kable_styling(full_width = FALSE, position = "left")

```
#### Not very informative


```{r check on one user,  cache = TRUE}

genz.lindsay <- genz.retweet[genz.retweet$name == "Lindsay", 
c("name", "created_at", "retweet_created_at", "retweet_screen_name", "retweet_name")]

knitr::kable(genz.lindsay, format = "html", row.names = TRUE) %>% kableExtra::kable_styling(full_width = FALSE, position = "left")

val <-  rtweet::search_tweets(q = "Valeria", n = 2500, lang="en")
dim(val)
val.df <- val[1:15, retweet.cols[c(3, 6, 10,11)]]
knitr::kable(val.df, format = "html", row.names = TRUE) %>% kableExtra::kable_styling(full_width = FALSE, position = "left")


```
### 



### exhibits strange column width if attempt is made to show every row

## Check what hash tags are used in relation to GM foods


```{r check on hash tags,  cache = TRUE}

gmft <-  rtweet::search_tweets(q = "#GM foods", n = 2500)
dim(gmft)

```

### no  entry that has text that is real English

```{r no text, cache = TRUE}
## if(nrow(gmft) > 0) 
## gmft[, c("text", "lang")]

## gm.dft <- gmft[, c(c(names(Zusrs)[c(3, 17, 50, 75, 61)]), "lang")]
## knitr::kable(gm.dft, format = "html", row.names = TRUE) %>% kableExtra::kable_styling(full_width = FALSE, position = "left")

## gmf$created_at 
## gmf$retweet_created_at 

  gmf <-  rtweet::search_tweets(q = "GM foods", n = 2500, lang="en")
dim(gmf)


```
### only 134. Still not enough to do much with

```{r gm chunk,  cache = TRUE}

gmff <-  rtweet::search_tweets(q = "#GeneticallyModified", n = 2500, lang="en")
dim(gmff)

```
### only 10

```{r gm2 chunk, cache = TRUE} 

gmff$name
gmff$screen_name

```
### Show all of small table with columns relating to retweeting

```{r  gm3 chunk, cache = TRUE}
gmff.df <- gmff[, retweet.cols] %>% arrange(created_at)

knitr::kable(gmff.df[, c("text", "created_at", "retweet_created_at", "is_retweet", "name", "retweet_text" )], format = "html", row.names = TRUE) %>% kableExtra::kable_styling(full_width = FALSE, position = "left")

```
### Look at some of the many columns

```{r GMO, cache = TRUE}

gmo <-  rtweet::search_tweets(q = "#GMO", n = 2500, lang="en") %>% arrange(created_at)
dim(gmo)
gmoT <- tail(gmo)

```
## Look at 15 rows of some other columns

```{r, echo = FALSE}
knitr::kable(gmo[1:15, c("text", "name", "retweet_text", "created_at", "retweet_created_at")], format = "html", row.names = TRUE) %>% kableExtra::kable_styling(full_width = FALSE, position = "left")

```
### And at the bottom of the table
	
```{r cache = TRUE}

knitr::kable(gmoT[, c("text", "name", "retweet_text", "created_at", "retweet_created_at")], format = "html", row.names = TRUE) %>% kableExtra::kable_styling(full_width = FALSE, position = "left")

### table(with(gmf, created_at - retweet_created_at), exclude = NULL)

## ```
library(PFRTextMiner)
## df <- rtweet::search_tweets("#GMO", n = 2500., lang = "en")# %>% arrange(created_at)

## # Process text column.
## df$processed_text <- PFRTextMiner::process_text(df$text)

## gmo_sent <- PFRTextMiner::mine_sentiment(text = gmo$text, by = "sentence")

```

### Create a new dataframe with a new column of words, not sentences 

```{r unnesting, cache = TRUE}

text_tok <- tidytext::unnest_tokens(tbl = gmo, 
                         output = word, 
                         input = text) 
dim(text_tok)
names(text_tok)

## look at some of that
display_tok <- text_tok[1:120, c("created_at", "word", "is_retweet")]

knitr::kable(display_tok, format = "html", row.names = TRUE) %>% 
       kableExtra::kable_styling(full_width = FALSE, position = "left") 

```
### (The same `retweet_created_at` appears numerous times since the consecutive rows come from the same sentence)
### What's different in column names?
```{r}
names_df <- data.frame(Tok = names(text_tok), Znorm = names(Zusrs))

names_df <- within(names_df,
                   TZ <- Tok %in% Znorm)
names_df <- within(names_df,
                   ZT <- Znorm %in% Tok)

## table(names(text_tok) %in% names(Zusrs))
knitr::kable(names_df, format = "html", row.names = TRUE) %>% 
   kableExtra::kable_styling(full_width = FALSE, position = "left") 

names(text_tok)[!names(text_tok) %in% names(Zusrs)]
names(Zusrs)[!names(Zusrs) %in% names(text_tok)]

```
#####  As is what's going on with `... output = word, input = text)`

##### No  surprises there. 



#### Observed effect of day of week on the number of GMO tweets

```{r DOW  frequency in GMO data, cache =  TRUE}

gmoT <- within(gmo, dow <- format(created_at, format = "%w")) %>% as.data.frame %>%
    select(text, dow, screen_name)
days <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
day.mat <- cbind("dow" = as.character(0:6),   "DOW" = days)
gmoT <- within(gmoT, DOW <- lookup(x = dow, y = day.mat))
gmoT <- within(gmoT, DOW <- factor(DOW, levels = days, labels = days))


gmo.dow.tab <- t(with(gmoT, table(DOW)))

knitr::kable(gmo.dow.tab, format = "html", row.names = FALSE) %>% 
   kableExtra::kable_styling(full_width = FALSE, position = "left")

```


### Get individual words from the `text` column, i.e. unnesting 


```{r unnestinmg, cache = TRUE}
words_df <- tidytext::unnest_tokens(tbl = gmoT, 
                          output = word, 
                          input = text) %>%
    count(screen_name, DOW, word, sort = TRUE)
## dim(words_df)
## ### omit stop words
## omitwords <-  tm::stopwords("en")
## words_df  <- words_df %>%
##             filter(!omitwords)
dim(words_df)
   

Total.words <- words_df %>%
    group_by(screen_name, DOW) %>%
    summarise(total = sum(n))



tweeter_words <- left_join(words_df, Total.words)
str(tweeter_words)
dim(tweeter_words)
head(tweeter_words)
tail(tweeter_words)

library(ggplot2)

```

```{r "setting the figure height", fig.dim = c(9, 6), out.width = "60%"}

library(ggplot2)
library(tidytext)

ggplot2::ggplot(tweeter_words, aes(n/total, fill = DOW)) +
  geom_histogram(show.legend = TRUE, binwidth = 0.025) + 
  labs(title = "Histogram #GMO Term frequency") + 
  facet_wrap(~DOW, ncol = 3, scales = "free_y")

```


#### similar pattern each day but quite variable in scale

##  **************************************************


## Try another query

### #cannabis


```{r frequency  term , cache =  TRUE}

###dim = c(9, 6), out.width = "60%"}
thc <-  rtweet::search_tweets(q = "#cannabis", n = 85000, lang="en") %>% 
   arrange(created_at)

thcT <- within(thc, dow <- format(created_at, format = "%w")) %>% as.data.frame %>%
    select(text, dow, screen_name)
days <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
day.mat <- cbind("dow" = as.character(0:6),   "DOW" = days)
thcT <- within(thcT, DOW <- lookup(x = dow, y = day.mat))
thcT <- within(thcT, DOW <- factor(DOW, levels = days, labels = days))

```

```{r print small table, cache = TRUE}

thc.dow.tab <- t(with(thcT, table(DOW)))

knitr::kable(thc.dow.tab, format = "html", row.names = FALSE, 
   caption = "A table of frequency of occurance of DOW") %>% 
   kableExtra::kable_styling(full_width = FALSE, position = "left")

```

```{r unnesting2, cache = TRUE}

words_df <- unnest_tokens(tbl = thcT, 
                          output = word, 
                          input = text) %>%
    count(screen_name, DOW, word, sort = TRUE)

Total.words <- words_df %>%
    group_by(screen_name, DOW) %>%
    summarise(total = sum(n))

tweet_words_thc <- left_join(words_df, Total.words)

tweeter_words <- left_join(words_df, Total.words)
str(tweeter_words)
dim(tweeter_words)
head(tweeter_words)
tail(tweeter_words)

library(ggplot2)
tweet_words_thc <- tweet_words_thc %>% bind_tf_idf(word, DOW, n)

```

```{r "setting the figure height: works now", fig.dim = c(7, 9), out.width="60%"}

library(ggplot2)
library(tidytext)

ggplot2::ggplot(tweeter_words, aes(n/total, fill = DOW)) +
  geom_histogram(show.legend = TRUE, binwidth = 0.05) +
  labs(title =  "Histogram Term frequency #cannabis") +
  facet_wrap(~DOW, ncol = 2, scales = "free_x")

```


#### (Shows the under-representation of Tuesday data points)

```{r lucky 2nd last, echo = TRUE, out.dim = c(7, 23), out.width="60%"}
tweet_words_thc %>% str
tweet_words_thc %>%
  arrange(desc(tf_idf)) %>% 
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(DOW) %>% 
  top_n(5) %>% 
  ungroup() %>%
  ggplot(aes(word, tf_idf, fill = DOW, binwidth = 0.05)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf_idf", title = "#cannabis Term frequency Inverted document frequency") +
  facet_wrap(~DOW, ncol = 2, scales = "free_y") +
  coord_flip()

## ```

## thcT <- within(thc, dow <- format(created_at, format = "%w")) %>% as.data.frame %>%
##     select(text, dow, screen_name)
## ## days <- c("Sunday", "Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday")
## ## day.mat <- cbind("dow" = as.character(0:6),   "DOW" = days)
## thcT <- within(thcT, DOW <- lookup(x = dow, y = day.mat))
## thcT <- within(thcT, DOW <- factor(DOW, levels = days, labels = days))







## words_df <- unnest_tokens(tbl = thcT, 
##                           output = word, 
##                           input = text) %>%
##     count(screen_name, DOW, word, sort = TRUE)

## Total.words <- words_df %>%
##     group_by(screen_name, DOW) %>%
##     summarise(total = sum(n))



## tweeter_words <- left_join(words_df, Total.words)
## str(tweeter_words)
## dim(tweeter_words)
## head(tweeter_words)
## tail(tweeter_words)

## library(ggplot2)

```


```{r, echo = TRUE, fig.width = 10, fig.height = 3, out.width="60%"}
words_df <- tidytext::unnest_tokens(tbl = thcT, 
                          output = word, 
                          input = text) %>%
    count(DOW, word, sort = TRUE)

Total.words <- words_df %>%
    group_by(DOW) %>%
    summarise(total = sum(n))

tweet_words <- left_join(words_df, Total.words)
library(ggplot2)

ggplot(tweet_words, aes(n/total, fill = DOW)) +
  geom_histogram(show.legend = TRUE) +
  xlim(NA, 0.0009) +
  facet_wrap(~DOW, ncol = 3, scales = "free_y")

tweet_words <- tweet_words %>%
  bind_tf_idf(word, DOW, n)

tweet_words
tweet_words %>%
  select(-total) %>%
  arrange(desc(tf_idf))

```

```{r lucky 2nd to last, echo = TRUE}
##, out.dim = c(7, 3)}
tweet_words %>% str
tweet_words %>%
  arrange(desc(tf_idf)) %>%
  mutate(word = factor(word, levels = rev(unique(word)))) %>% 
  group_by(DOW) %>% 
  top_n(5) %>% 
  ungroup() %>%
  ggplot(aes(word, tf_idf, fill = DOW, binwidth = 0.01)) +
  geom_col(show.legend = FALSE) +
  labs(x = NULL, y = "tf-idf") +
  facet_wrap(~DOW, ncol = 3, scales = "free") +
  coord_flip()


knitr::kable(thc[1:50, c("text", "created_at", "retweet_created_at", "is_retweet", "name", "retweet_text" )], format = "html", row.names = TRUE) %>% kableExtra::kable_styling(full_width = FALSE, position = "left")


```




---
